---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ADS8192 Heatmap Package

<!-- badges: start -->
[![R-CMD-check](https://github.com/akaur40/ADS8192/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/akaur40/ADS8192/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

This package provides tools for analyzing RNA-seq data from the fission yeast stress response experiment. It includes functions to do the following:
- Normalize count data
- Select top variable genes
- Scale expression matrices
- Generate annotated heatmaps
- Extract gene modules
- Export results

## Installation

You can install the development version of ADS8192 from [GitHub](https://github.com/) with:

``` r
remotes::install_github("akaur40/ADS8192")
```

## Quick Start Guide

```{r example}
devtools::load_all()

#load example data
data("example_se", package = "ADS8192")

#Run full analysis
result <- run_heatmap_analysis(example_se)

#view output
result$heatmap
head(result$scaled_matrix)
head(result$gene_modules)
```

#Example with parameters

```{r}
devtools::load_all()
data("example_se", package = "ADS8192")

result <- run_heatmap_analysis(
  se = example_se,
  n_top = 500,
  scale_method = "zscore",
  gene_k = 5,
  column_split_by = "strain"
)
```

## Command Line Interface (CLI)

This package provides a command-line interface for running the analysis
Install the CLI launcher:
```{r}
ADS8192::install_ads8192_cli()
```

CLI help:
```{bash, eval=FALSE}
ADS8192 heatmap --help
```

Fallback development usage:
```{bash, eval=FALSE}
Rapp exec/ADS8192.R heatmap --help
```

Example run:
```{bash, eval=FALSE}
ADS8192 heatmap \
  --input example \
  --n_top 500\
  --scale_method zscore \
  --gene_k 5 \
  --column_split_by strain \
  --output_dir results/
```

